Scaling laws of trophic level and generality vary across latitude

### 2014-07-04 manuscript/latitudepaper.tex
Fixed food web properties, edited manuscript. New story entirely now.

I want to know: Does latitude affect scaling of generality with species richness?

Considerations: Data quality (S<5 for some webs), model (log, nls, nlme)

2) Add more webs (Riede 2010).
    - pred-prey components of 7 parasite estuary webs
    - Baird\&Ulanowicz - will need to be entered by hand (old pdf) - good quant web for concomitant project
    - Heymans - look carefully at which webs to include, aggregate
    - 
3) Gen probably doesn't need to include connectance (LS doesn't, plus I don't actually care)
5) LS, Gen (to compare more directly w mutualists) first.

@@

Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Williams2000,earlierwork}.
Comparisons of community structure around the world and across ecosystem types 
have revealed that the structure of biological networks is generally tightly
constrained, particularly by relationships between species richness or connectance
(the proportion of possible links that are realized) and other food-web properties \citep{Riede2010}.
These relationships have suggested that the structure of food webs is highly scale-dependent. 
Specifically, network properties such as fractions of species in different trophic groups 
have been shown to strongly depend on the species richness or connectance of
the networks \citep{Vermaat2009,Riede2010}.

As changes in species richness and connectance can explain much of the variation in network structure \citep{Vermaat2009}, 
it follows that drivers of change in these two properties may also affect other properties. Species richness in particular 
exhibits a strong latitudinal gradient, believed to be driven by varying productivity and temperature at different latitudes 
\citep{Hawkins2004,Cardillo2005,Thompson2005,Davies2007}. An alternative view
posits that species' niches are narrower in the tropics, 
reducing competition and permitting greater adaptive radiation \citep{}. Although this view is only equivocally supported 
\citep{Vazquez2004}, it is also possible that the higher productivity of the tropics \citep{Brown2004} may result in a broader 
niche space \citep{Davies2007} which could also allow greater diversification even if niche sizes are globally similar.

In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
generality of associations between biological processes and environmental variables, suggest that variation in network structure 
may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
changing species richness.

Here we examine the effect of latitude on food-web structure by examining
its impact on the scaling relationships of food-web properties with species
richness and connectance. We expect that food-web structure will scale strongly
with both species richness and connectance, and that the scaling relationships
of properties measuring degree of specialization (i.e., generality, vulnerability, and
links per species) will change over latitude. The scaling relationships of other
properties (for example the proportions of top, intermediate, and basal resources) may
be less affected by latitude.

>>>>

@@

%Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Williams2000,earlierwork}.
One of the earliest goals of constructing food webs was to measure the relationship between the species richness of
a community and its stability \citep{Dunne2006}, a goal which is still pursued today \citep{robustness studies}.
Some authors have recognized the potential for environmental effects to influence stability \citep{Shurin2007}, as well as other food web properties such as food chain length \citep{Townsend1998,Thompson2003,2004c,Young2013,Digel2014}.
Latitude is a particularly intruiging contender for an environmental influence on food web structure \citep{Shurin2007},
as latitudinal gradients in temperature \citep{}, primary productivity \citep{}, body size \citep{}, and 
species richness \citep{Schemske2009a} are among the most robust patterns in ecology[[back up from original draft]].

Latitude's strong influence on species richness, however, presents a problem for the analysis of food web structure.
Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
analyses with higher-quality data have revealed that most food-web structural properties scale strongly with species 
richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that relationships
between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
This is especially true for food-web properties that both scale with species richness and are related to candidate
explanations for the latitudinal diversity gradient.

% Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
%Then give hypotheses.
Here, we are particularly interested in the potential effects of latitude on scaling relationships for the number of
links per species, generality (the number of prey per predator), and vulnerability (the number of predators per prey).
We focus on these properties because they are related to one of leading candidates for a mechanism behind the 
latitudinal species-richness gradient: namely that species' niches are narrow in the tropics, reducing competition
and permitting greater adaptive radiation (reviewed in \citet{Vazquez2004}). Alternatively, it is  possible that the
higher productivity of the tropics \citep{Brown2004} may result in a broader 
niche space \citep{Davies2007} which could also allow greater diversification even if niche sizes are globally similar.
In either case, if there is less competition at lower latitudes, there should also be less generality. A higher 
proportion of non-competing specialists should also result in lower vulnerability.
Importantly, these trends (lower generality, vulnerability, and hence links per species in the tropics) are opposite
to those based on the positive scaling relationship between links per species and species richness \citep{Riede2010}.
If, therefore, there is a latitudinal effect on generality and vulnerability beyond that of the latitudinal diversity
gradient, the scaling relationships between species richness and links per species, generality, and vulnerability 
should vary over latitude.

%Among other things, a constant scaling between S and C implies that species tend to eat the same number of prey regarless of diversity \citep{Dunne2006,Pimm1982} - rephrase a bit more, this is very close.

% In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
% rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
% generality of associations between biological processes and environmental variables, suggest that variation in network structure 
% may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
% on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
% example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
% latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
% related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
% changing species richness.
